\documentclass{article}
\usepackage{fullpage}
\usepackage{times}
\usepackage{cite}
\usepackage{hyperref}
\usepackage{algorithmic}
\usepackage{amssymb}
\usepackage{algorithm}
\usepackage{adjustbox}
\usepackage{graphicx}

\newcommand{\code}[1]{\texttt{#1}}
\begin{document}

\begin{center}
    \vspace{2cm}
    \huge { Thesis Preparation Report \\ }
    \vspace{2cm}
    \large {Magnus Stahl (msta@itu.dk)\\
    IT-University of Copenhagen\\
    Fall 2016}
\end{center}


\tableofcontents


\section{Introduction}
 
This report details introductory thesis work as part of a spring 2017 thesis at the IT-University of Copenhagen. The report will describe the work undertaken so far, and a plan for how the thesis will be completed in the spring. \\

The topic of the thesis can be formulated with the following research questions:
\begin{itemize}
    \item What are the current state-of-the-art systems for relation classification 
    with neural networks?\\
    \item Is it possible to simplify structures in state-of-the-art systems while maintaining (or increasing) the F1 metric?
\end{itemize}


The task of relation classification can be defined as:
Given a sentence $S$ and two labeled entities \textless e1\textgreater  and \textless e2\textgreater , classify the relation between the entities and the (sometimes optionally) ordering of the relation. Here is an example:

Given sentence $S$: \emph{``The train rolled onto the platform with a peculiar choo choo.''}
and entities \textless e1 \textgreater \emph{train}, \textless e2 \textgreater \emph{platform} the relation is of the form Entity-Destination(e1,e2).

Neural networks are a group of data structures and related algorithms that loosely models features of a biological brain.  


\subsection{Motivation}

This section motivates why the subject of the thesis is important and interesting.\\

Relation classification is a hard task for computers. Correctly classifiying entities in language requires understanding the context of the entities as well as an abstract understanding
of their relationship. Recent deep learning experiments have yielded excellent results compared to feature-based classifiers, which require feature engineering.   

Neural networks are interesting in NLP because they allow features to be learned automatically
from raw input data. 

Simplification of state-of-the-art systems are necessary because the newest systems are
often built on top of other state-of-the-art systems. These ``research iterations'' often
lead to including substructures from previous systems which might not be relevant in the newer system. Additionally, hyperparameters are not always decided by search but rather by sticking to values which were chosen in a previous system. Hyperparameters might incur unnessecary memory or performance costs. Finally, it may be the case that simpler networks generalize better to other related tasks (INSERT REFERENCE).  


\section{Work so far}

Word embeddings have done such and such
cite different papers here

Convolutional neural networks have done stuff

And other recurrent structures such as LSTM


This section details the work which has been done until now. 



\subsection{Research done}

The material I have investigated are grouped into two broad categories: general educational material about deep learning in NLP, and recent research about neural networks in relation classification in particular,  


Papers read and problems along the way...?


\subsection{Implementation and current baseline}

I'll wait with this until just before the hand-in I guess.


\section{Thesis plan}

\ref{att_cnn}
\cite{att_cnn}
Gant diagram including,
Implementing pairwise margin-based loss function

Attention-based pooling
Contextual embeddings?

Proper baseline description
Construct PROPER table of hyperparameters for ALL LAYERS!!!!!

Investigate named-entity recognition multi-training(?)

Semantic relation stuff, going from general relations to specific
sets (legal documents)

Try cutting off 1 entity and then classifying the relation along with the other entity?


\bibliographystyle{plain}
\bibliography{Bibliography}


    
\end{document}

